---
title: "index"
author: "Jennifer Bone, Jennifer Kidson, Julia Paltseva"
date: "January 27, 2016"
output: html_document
---

# Citizen Monitoring
________________________________________
## Types of data
Data collected will consist of text survey responses. Information will include phone numbers, timestamp, location information, demographic information, and a survey response, which may be numeric or text. Data will be coded to ensure anonymity of respondents. 

The data will be categorized according to which survey question they are answering. This will be done with the timestamp data that comes in with each survey response. Once responses are separated into the proper questions, summary statistics will be generated for each one.
 
## Data and metadata standards
Metadata will include explanations of each of the following category headings: nominated, zone, years_zone, gender, age, and satisfaction.
 
## Policies for access and sharing
Since some versions of this data are tied to specific survey respondents (via telephone number) it should not be shared in a raw format. Statistics generated from the data may be shared in accordance with PI's instructions.

## Policies and provisions for re-use, re-distribution
To be specified by PI.

## Plans for archiving and preservation of access
To be specified by PI.

## Data Question
How many women are very satisfied with solid waste collection?

```{r}
# load libraries
library(readr)
library(dplyr)

# read in csv
response = read.csv('data/ugandasms.csv') 

# using dplyr
response %T>%                          # note tee operator %T>% for glimpse
  glimpse() %>%                        # view data
  select(gender, satis) %>%            # limit columns
  filter(gender  == 'female') %>%      # limit rows
  group_by(satis) %>%                  # get count by first grouping
  summarize(n = n()) %>%               # then summarize
  write_csv('data/f_satis.csv')        # write out csv
  summary(response)
```

What is the age distribution of survey participants?

```{r}
#read in csv
response2 = read.csv('data/ugandasms.csv')

hist(response2$age, main = "Age Distribution of Survey Participants", xlab = "Age", ylab = "Frequency")
```


How many men are dissatisfied with trash collection services?

```{r}
# load libraries
#library(readr)
#library(dplyr)

#read in csv
response2 = read.csv('data/ugandasms.csv')

response2 %T>%                         # note tee operator %T>% for glimpse
  glimpse() %>%                        # view data
  select(gender, satis) %>%            # limit columns
  filter(gender  == 'male') %>%        # limit rows
  group_by(satis) %>%                  # get count by first grouping
  summarize(n = n()) %>%               # then summarize
  write_csv('data/m_dissat.csv')       # write out csv
  summary(response2)
```

There are 198 men who are dissatisfied with trash collection services in the baseline survey.
>>>>>>> 076cbbca7902c2d7b782f01a087f254c9200ff79

<<<<<<< HEAD
Which zone has the most dissatisified survey respondents?
```{r}
library(dplyr)
library(readr)
#read in csv
response3=read.csv('data/ugandasms.csv')
View(response3)

#using dplyr
response3 %T>%
  select(satis,Zone) %>%
  filter(satis == "very_dissatisf") %>%
  group_by(Zone) %>%
  summarize(n = n()) %>%
  write_csv('data/zonedissatis.csv')
  summary(response3)
```

=======